Reviewer comments from PeerJ

### 2015-03-02 PeerJResponse.tex
Edits to responpse
Reviewer 2, comments

@@

\lev{I think that we did initially to check. But all of the products match the appropriate and expected size. The only issue we had was suddenly the different size with the Pif, which we did check with sequencing.}

\mbh{we need to check this.  can you go back through emails or to your lab notebook to find whether this was sequenced?}
\jri{i don't remember ever checking this. we checked the pif by PCRing stuff John had already sequenced in which i identified the pif}
\lev{I agree with Jeff. I believe bands matched with what was expected based on where we designed primers so we did not sequence them}

>>>>

\lev{changed to be within manuscript. sizes added to figure legend}

@@

\lev{The only sequence data we have was when we sequenced a bit of the Pif to make sure that was what it was.}

\res{We did not sequence PCR products. We felt this was unnecessary based on the fact that primers were designed off of previous maize and teosinte sequence data. Furthermore, primers are unique to their location in the genome and do not BLAST with any confidence to any other location in the maize genome. PCRs produced bands of the expected sizes, which we felt was adequate.}
